Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2015-03-14 sas2015/content/impl.tex
Revert "evaluation"
This reverts commit 378e84e1c21b63e748965ae7a167c997cd1ec0b5.

%\subsection{Implementation of the Correlated-Calls Analysis}
\section{Evaluation}
We implemented the correlated-calls analysis in Scala~\cite{odersky2004overview}. 
Our implementation analyzed Java bytecode compiled from input programs written
in Java.
%The input programs that we analyzed were written in Java. Our implementation analyzed the
%corresponding Java bytecode.
We used WALA~\cite{fink2012wala}
to retrieve information about an input program, such as its control-flow supergraph and the set of receivers and their types.
Since WALA does not contain an implementation of the IDE algorithm,
we implemented it from scratch.
%currently only contains an implementation of IFDS, we implemented IDE from scratch.
We will submit our implementation to the artifact evaluation committee, and we are working on integrating it and contributing it officially to WALA. % Instead of using WALA's IFDS implementation, to run an IFDS problem, we converted it to an IDE problem and used our own IDE solver.

@@

The average running time for small programs such as in Figure~\ref{list:ccexample} is ???~seconds. On the SPECjvm98 benchmarks, the average running time is ???~seconds. So far we were only able to find a practical benefit from the correlated-calls analysis for programs in which correlated calls were ``artificially'' introduced in control-flow paths relevant to the specific client analysis. We are still working on identifying in which client IFDS problems, in combination with which benchmarks, we would encounter a precision improvement.

>>>>

\subsection{Implementation of the Correlated-Calls Analysis}
We implemented the correlated-calls analysis in Scala~\cite{odersky2004overview}. 
Our implementation analyzed Java bytecode compiled from input programs written
in Java.
%The input programs that we analyzed were written in Java. Our implementation analyzed the
%corresponding Java bytecode.
We used WALA~\cite{fink2012wala}
to retrieve information about an input program, such as its control-flow supergraph and the set of receivers and their types.
Since WALA does not contain an implementation of the IDE algorithm,
we implemented it from scratch.
%currently only contains an implementation of IFDS, we implemented IDE from scratch.
We will submit our implementation to the artifact evaluation committee, and we are working on integrating it and contributing it officially to WALA. % Instead of using WALA's IFDS implementation, to run an IFDS problem, we converted it to an IDE problem and used our own IDE solver.

@@
